Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-25 paper/Draft.tex
Add IQR var for SCE
SCE IR analysis results generated.But not debugged.

\begin{figure}[h]\label{IQR_Unceratitny}
	\centering
	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
	\smallskip
	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
	\includegraphics[width=8cm]{figures/IQRvarSCEQ.png}\\
	\caption{Dispersion in Mean Forecast and Unceratinty }
\end{figure}

@@

\begin{figure}[h]\label{ReplicateCoibionpost2007}
	\centering
	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_nmp_post2007.png}  
	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_post2007.png} \\
	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_post2007.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_post2007.png} \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_post2007.png} \\
	\smallskip 
		\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_post2007.png} 
	\caption{ Replicating \cite{coibion2012can}: 2008-2019}
\end{figure}

>>>>

\begin{figure}[h]\label{IQR_Unceratitny}
	\centering
	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
	\smallskip
	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
	\includegraphics[width=8cm]{figures/IQRvarSCEM.png}\\
	\caption{Dispersion in Mean Forecast and Unceratinty }
\end{figure}

@@

\begin{figure}[h]\label{ReplicateCoibionpost2007}
	\centering
	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_nmp_post2007.png}  
	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_post2007.png} \\
	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_post2007.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_post2007.png} \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_post2007.png} \\
	\smallskip 
		\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_post2007.png} 
	\caption{ Replicating \cite{coibion2012can}: 2008-2019}
\end{figure}

\begin{figure}[h]\label{SCE_IR}
	\centering
	\includegraphics[width=3cm,height=2cm]{figures/CPIAU_ashocks_nmpM.png}  
	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocksM.png} \\
	\smallskip
	\includegraphics[width=3cm,height=2cm]{figures/SCEFE_ashocks_nmpM.png} 
	\includegraphics[width=6cm,height=2cm]{figures/SCEFE_ashocksM.png} \\
	\smallskip
	\includegraphics[width=3cm,height=2cm]{figures/SCEDisg_ab_ashocks_nmpM.png} 
	\includegraphics[width=6cm,height=2cm]{figures/SCEDisg_ab_ashocksM.png} \\
	\smallskip 
	\includegraphics[width=3cm,height=2cm]{figures/SCEVar_ab_ashocks_nmpM.png} 
	\includegraphics[width=6cm,height=2cm]{figures/SCEVar_ab_ashocksM.png} 
	\caption{ Impulse Responses of Inflation and SCE Forecasts to Inflation Shocks}
\end{figure}
